Source Summaries

### 2020-02-09 paper/sourceSummaries/summary1.tex

\noindent
The authors outline how to approach attacking Bluetooth locks in a scientific fashion. They use well documented attacks and threat modeling to discover vulnerabilities in a Bluetooth low energy lock.

@@

\noindent
A threat rating system following the DREAD model is created to accurately represent the threat of the lock. Three threat models were created: unauthorized lock access, avoidance of logging, and denial of service. A Bluetooth man in the middle attack is carried out to gather information about the lock’s Generic Attribute Profile (GATT), how connections are formed, hosted services, and other characteristics of the lock. Using the GATT, a fake lock can be created to connect to the application, and then forward all information onto the actual lock. Next, access permission edge cases are tested to see when access can be abused to bypass controls. The app was reversed to gather further insight on how the app connected to the lock.

@@

\noindent
Not much was able to be done in the way of breaking into the lock. Some patterns were found in the communication scheme, but nothing to indicate how the data was being encrypted. A replay attack was launched, but this was ineffective. Fuzzing was similarly ineffective. If an attacker is granted permission to access the lock, disconnects their internet, and then their permission is revoked, the attacker can still access the lock. In the app, a possible encryption key for a database was found, but not pursued.

>>>>

\noindent
The authors outline how to approach attacking Bluetooth locks. They use well documented attacks to discover vulnerabilities in a Bluetooth low energy lock.

@@

\noindent
The authors create a threat rating system following the DREAD model is to accurately represent the threat of the lock being successfully attacked. They make three threat models: unauthorized lock access, avoidance of logging, and denial of service. They use a Bluetooth man in the middle attack to gather information about the lock’s Generic Attribute Profile (GATT), how the application connected to the lock, hosted services, and other characteristics of the lock. Using the GATT, an attacker could use a fake lock hosted on a Arduino board to connect to the application, and then forward all information to the actual lock. Next, the authors test access permission edge cases to see when access could be abused by an attacker to bypass controls. The authors then reversed the app to gather further insight on how the app connected to the lock.

@@

\noindent
Not much was able to be done in the way of breaking into the lock. Some patterns were found in the communication scheme, but nothing to indicate how the application was encrypting the connection. The authors lauched a replay attack, but this was ineffective. Fuzzing was similarly ineffective. If the owner of the lock granted an attacker permission to access it, disconnects their internet, and then the attacker's permission was revoked, the attacker can still access the lock. In the app, a possible encryption key for a database was found, but not pursued.

### 2020-02-09 paper/sourceSummaries/summary2.tex

>>>>

\noindent
Connor Leavesley

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry

\bibentry{sevier2019securityofble}

\noindent
The authors aim to explain how Bluetooth LE protocol works and the cryptographic weaknesses in the protocol.

\noindent
This paper is applying Game Theory. A successful cryptographic attack is a loss for the security of the protocol.

\noindent
The authors first sniffed the Bluetooth traffic with a Ubertooth using the BlueZ Bluetooth driver and associated Ubertooth drivers. Using the Blueooth handshake, the authors used Crackle to crack the Temporary Key due to its restricted key space. The Temporary Key was then used to gain access to the Long Term Key (LTK). The LTK was then used to decrypt any future communication traffic in Wireshark.

\noindent
The authors found that the keyspace of the Temporary Key is very restricted, allowing for a very quick brute force attack. They also found that Bluetooth Low Energy was susceptible to a number of attacks due to the low power requirements: denial of service and replay attacks. It was also found that Ubertooth struggled to capture a complete pairing event. The authors suggest that the Ubertooth should be as close as possible to the source transceiver to mitigate this issue.

\noindent
Many vendors likely do not implement the Bluetooth stack correctly. These vendors may also use the same stack across multiple devices. Areas of further research should focus on individual devices from the same vendor to attempt to find vulnerabilities that affect entire product lines.
